Analysis of Competence Index

### 2017-05-10 analysis/analysis_competence.Rmd
update latex and fig

$$\sum_{i=1}^{n}pi\cdot (dbh_{i} / 2)^2$$

@@

#### San Juan 
```{r, echo=FALSE}
# see stackoverflow questions 6862742
gg_circle <- function(radius, xcenter, ycenter, color='black', fill=NA, ...){
  x <- xcenter + radius*cos(seq(0,pi, length.out = 100))
  ymax <- ycenter + radius*sin(seq(0, pi, length.out = 100))
  ymin <- ycenter + radius*sin(seq(0, -pi, length.out = 100))
  annotate("ribbon", x=x, ymin=ymin, ymax=ymax, color=color, fill=fill, ...)
}

@@

#### Canar 
```{r, echo=FALSE, fig.height=8, fig.width=12}
compete %>%  
  filter(sp != 'Focal') %>%
  filter(loc == 'CA') %>% 
  ggplot(aes(x=xcord, y=ycord)) + 
  facet_wrap(~id_focal) + 
  geom_point(aes(size=dn), shape=21, fill='transparent') +
  xlim(-11,11) + ylim(-11,11) + 
  geom_point(aes(x=0, y=0), color='green') +
  theme_bw() +
  gg_circle(radius = 10, xcenter = 0, ycenter = 0) +
  theme(panel.grid.major=element_blank(), 
        panel.grid.minor=element_blank(), 
        strip.background = element_rect(colour = "black", fill ='transparent')) 
```

>>>>

$$ \sum_{i=1}^{n}pi\cdot (dbh_{i} / 2)^2 $$

@@

#### San Juan 
```{r, echo=FALSE, fig.height=8, fig.width=10}
# see stackoverflow questions 6862742
gg_circle <- function(radius, xcenter, ycenter, color='black', fill=NA, ...){
  x <- xcenter + radius*cos(seq(0,pi, length.out = 100))
  ymax <- ycenter + radius*sin(seq(0, pi, length.out = 100))
  ymin <- ycenter + radius*sin(seq(0, -pi, length.out = 100))
  annotate("ribbon", x=x, ymin=ymin, ymax=ymax, color=color, fill=fill, ...)
}

@@

#### Canar 
```{r, echo=FALSE, fig.height=9, fig.width=12}
compete %>%  
  filter(sp != 'Focal') %>%
  filter(loc == 'CA') %>% 
  ggplot(aes(x=xcord, y=ycord)) + 
  facet_wrap(~id_focal) + 
  geom_point(aes(size=dn), shape=21, fill='transparent') +
  xlim(-11,11) + ylim(-11,11) + 
  geom_point(aes(x=0, y=0), color='green') +
  theme_bw() +
  gg_circle(radius = 10, xcenter = 0, ycenter = 0) +
  theme(panel.grid.major=element_blank(), 
        panel.grid.minor=element_blank(), 
        strip.background = element_rect(colour = "black", fill ='transparent')) 
```
